%Abstract
\addcontentsline{toc}{chapter}{Abstract}
\chapter*{ABSTRACT}
\pagenumbering{roman}
\hspace*{0.3in}
Quantum computing (QC) and artificial intelligence (AI) are coming together in an exciting way, shaking up the tech world, also called as  Quantum Artificial Intelligence (QAI). AI is stepping up to improve how quantum systems are designed, fix errors, and fine-tune algorithms, while QC is turbocharging AI tasks like training machine learning models and tackling tough simulations. In this paper, I dive into how AI is making a difference in QC, think calibrating quantum processors, cutting noise with reinforcement learning, and blending quantum-classical models for big language processing. I also explore some key trends for 2025, the UN’s International Year of Quantum Science and Technology, like scalable error-corrected qubits (check out Google’s Willow chip!), modular setups with over 1,000 qubits, and quantum networks that enable distributed computing.
This paper checks out some really cool real-world uses, like drug research, banking, and cybersecurity, while facing down challenges like qubit decoherence and a real crunch for skilled folks. From what I have found, AI teamed up with quantum computing might just give us a leg up in specialized areas by 2029, unlocking breakthroughs for those tricky problems. But honestly, cracking those scaling issues will take a group effort from all sorts of experts. This study lays out a solid picture for researchers and practitioners, with an eye on the exciting road ahead in this ever-changing field.
\\
\textbf{Keywords: Quantum Computing, Artificial Intelligence, Quantum AI Synergy, Error Correction,
	Reinforcement Learning, Hybrid Models, Qubit Scalability, Quantum Networks, Drug
	Discovery, Financial Optimization, Cybersecurity, Quantum Advantage, NISQ Devices,
	Fault-Tolerant Computing, Machine Learning Acceleration.
}\\