\chapter{REAL-WORLD APPLICATIONS: CASES \& EVIDENCE}

\hspace*{0.3in}Quantum Artificial Intelligence (QAI) has moved beyond theory into demonstrable real-world applications. This section highlights representative cases across drug discovery, healthcare, finance, and cybersecurity, where hybrid quantum–AI approaches are starting to show tangible value.

\section{Drug Discovery \& Molecular Simulation}
\hspace*{0.3in}QAI is showing strong promise in drug discovery, where accurate molecular simulations are critical. By combining quantum simulation with AI optimization, researchers can model protein–ligand interactions more precisely, reducing the time needed to identify drug candidates [9]. Hybrid QAI workflows are already being tested by pharmaceutical companies, aiming to cut costs and accelerate therapeutic development.
\section{Healthcare: Diagnostics \& QML for Limited Data}
\hspace*{0.3in}In healthcare, QML has proven effective when data is scarce. A lung cancer prediction study using Pegasos QSVC reached 85\% accuracy [10], outperforming classical methods on small datasets. Similar approaches are being explored for genomics, imaging, and personalized medicine, where QAI can enhance diagnostics and reduce false positives.
\section{Finance \& Cybersecurity}
\hspace*{0.3in}Finance and cybersecurity benefit from QAI’s ability to handle complex optimization and anomaly detection. In finance, quantum-enhanced models improve portfolio optimization and risk analysis. In cybersecurity, QAI supports fraud detection and intrusion modeling, with quantum GANs being tested for predictive defense strategies. These early cases show how QAI can strengthen resilience in data-intensive industries.