\chapter{ CYBER SECURITY}



\hspace*{0.3in} cyber security refers to the practices and measures taken to protect computer systems, networks, and data from unauthorized access, attacks, and damage. It involves implementing various techniques like encryption, firewalls, and secure authentication to safeguard against cyber threats such as hacking, malware, and data breaches. Cyber security is crucial in ensuring the confidentiality, integrity, and availability of information in the digital world. It helps protect individuals, organizations, and even social media platforms from potential risks and vulnerabilities.

Social media takes a major role in the present society.
People enable them keep to be connected with each other in a
better manner and make new opportunities for their business.
In the present, many people are using social media in a high
percentage. Recently, the internet is the most growing
technology for almost everyone's everyday uses. With Internet
technology, everyone around the world can communicate,
exchange information, play, and many other Internet uses in a
simple and semi-free manner, even with very limited
information technology experience . Social media is a
series of Web pages focused on the Internet. Social media’s
purpose and the role is to facilitate the personal as well as
business-focused engagement people of around the world.
Social networking is a tool that enables content sharing
between users. The contents are different types of information
on a range of topics. In addition, the service also helps users
to exchange new concepts, thoughts, and experiences with
many people. Many social media forms, networks and
services are available nowadays, including Facebook,
Instagram, YouTube, LinkedIn, Twitter, and snapchat.

 Cyber security is like having a digital bodyguard that protects your personal information, online accounts, and devices from cybercriminals. It involves using techniques such as encryption, strong passwords, and secure networks to keep your data safe. Cyber security also helps prevent unauthorized access, identity theft, and other cyber threats. It's like having a shield that keeps you safe in the digital world.

 \section{How does Cyber Security make working so 
easy? }
\hspace*{0.3in}No hesitation that the tool of Cybersecurity 
makes our work very easy by ensuring the 
obtainability of the capitals limited in any network. A 
commercial or society could look a huge damage if 
they are not honest about the safety of their online 
occurrence. In today’s linked world, everyone aids
from progressive cyber defence agendas. At a 
separate level, a cybersecurity outbreak can result in 
entirety from individuality theft, to blackmail 
attempts, to the damage of vital data similar family 
photographs. Everybody relies on dangerous 
structure like influence plants, infirmaries, and 
monetary service businesses. Securing these and 
other societies is essential to trust our civilization 
operative. One and all also remunerations from the 
work of cyberthreat investigators, similar the team of 
250 risk investigators at Talos, whoever explore new 
and developing fears and cyber bout policies. They 
disclose new susceptibilities, teach the community on 
the position of cybersecurity, and toughen open 
source gears. Their work marks the Internet harmless 
for one and all.
\\
\section{Cyber Ethics}
\hspace{0.3in}Cyber ethics are nothing but the code of the 
internet. When we practice these cyber ethics 
there are good chances of us using the internet 
in a proper and safer way. The below are a few 
of them:
\begin{enumerate}
	\item DO use the Internet to communicate 
	and interact with other people. Email 
	and instant messaging make it easy to 
	stay in touch with friends and family 
	members, communicate with work 
	colleagues, and share ideas and 
	information with people across town or 
	halfway around the world.
	\item Don’t be a bully on the Internet. Do not 
	call people names, lie about them, send 
	embarrassing pictures of them, or do 
	anything else to try to hurt them.
	\item Internet is considered as world’s largest 
	library with information on any topic in 
	any subject area, so using this 
	information in a correct and legal way 
	is always essential.
	\item Do not operate others accounts using 
	their passwords. 
	\item Never try to send any kind of malware 
	to other’s systems and make them 
	corrupt.
	\item Never share your personal information 
	to anyone as there is a good chance of 
	others misusing it and finally you 
	would end up in a trouble.
	\item When you’re online never pretend to 
	the other person, and never try to create 
	fake accounts on someone else as it 
	would land you as well as the other 
	person into trouble.
	\item Always adhere to copyrighted 
	information and download games or 
	videos only if they are permissible.
	The above are a few cyber ethics one must 
	follow while using the internet. We are always 
	thought proper rules from out very early stages 
	the same here we apply in cyber space.
\end{enumerate}








