\chapter{ ROLE OF CYBER SECURITY IN SOCIAL MEDIA  
}
\hspace*{0.3in}As we become more social in an increasingly 
connected world, companies must find new 
ways to protect personal information. Social 
media plays a huge role in cyber security and 
will contribute a lot to personal cyber threats. 
Social media adoption among personnel is 
skyrocketing and so is the threat of attack. Since 
social media or social networking sites are 
almost used by most of them every day it has 
become a huge platform for the cyber criminals 
for hacking private information and stealing 
valuable data. 
\\
\hspace*{0.3in}In a world where we’re quick to give up our 
personal information, companies have to ensure 
they’re just as quick in identifying threats, 
responding in real time, and avoiding a breach 
of any kind. Since people are easily attracted by 
these social media the hackers use them as a bait 
to get the information and the data they require. 
Hence people must take appropriate measures 
especially in dealing with social media in order 
to prevent the loss of their information.
The ability of individuals to share information 
with an audience of millions is at the heart of the 
particular challenge that social media presents to 
businesses. In addition to giving anyone the 
power to disseminate commercially sensitive 
information, social media also gives the same 
power to spread false information, which can be 
just being as damaging. The rapid spread of 
false information through social media is among 
the emerging risks identified in Global Risks 
2013 report.\\

\hspace*{0.3in}Though social media can be used for cyber 
crimes these companies cannot afford to stop 
using social media as it plays an important role 
in publicity of a company. Instead, they must 
have solutions that will notify them of the threat 
in order to fix it before any real damage is done.
However companies should understand this and 
recognise the importance of analysing the 
information especially in social conversations 
and provide appropriate security solutions in 
order to stay away from risks. One must handle 
social media by using certain policies and right 
technologies.\\
\section{Cyber Crime}
\hspace{0.3in}Cyber crime is a term for any illegal activity that 
uses a computer as its primary means of 
commission and theft. The U.S. Department of 
Justice expands the definition of cyber crime to 
include any illegal activity that uses a computer 
for the storage of evidence. The growing list of 
cyber crimes includes crimes that have been 
made possible by computers, such as network 
intrusions and the dissemination of computer 
viruses, as well as computer-based variations of 
existing crimes, such as identity 
theft, stalking, bullying and terrorism which 
have become as major problem to people and 
nations. Usually in common man’s language 
cyber crime may be defined as crime committed 
using a computer and the internet to steel a 
person’s identity or sell contraband or stalk 
victims or disrupt operations with malevolent 
programs. As day by day technology is playing 
in major role in a person’s life the cyber crimes 
also will increase along with the technological 
advances
\\

