\chapter{LITERATURE SURVEY	}

\section{	Need of Soial Media}
\hspace*{0.3in}Why do we need social media? Social media accept a bond
building between users from distinct backgrounds, resulting in
a tenacious social structure . However, according to 
currently websites of social networking have become an active
ground for cybercriminals. So does social media have positive
or negative effects? According to  Social media is one form
of communication which has both positive and negative
effects for its users . This study has been able to convey
both positive and negative effects of social media to users
clearly[1].
\\
\section{	Role of security in social media}
\hspace*{0.3in}One of the biggest disadvantages of social media is the issue
of privacy and security. But why exactly we need security in
social media. In spite of the security of social media is a now
widely-studied subject, there still does not seem to be a
consensus for exactly why we need social media security. It
was checked that most consumers are generally unaware of
the fact that the numerous privacy risks involved in posting
personal information on social networking websites are
widespread. But has mentioned that, Social media
prominence is such that active social media users around the
3
world are projected to reach some 2.95 billion by 2020 .
However, there’s quite less information on why social media
security is needed in this paper[3]. 

\\
\section{Access and usage of Social Media}
\hspace{0.3in}In general, users may use their personal computers or
mobile devices to access social media services through web
based technologies [1]. Such accesses to websites of social
media allow users to have an account or build their own
accounts through some authentication and compliance with
policies. The verification involves special information about
an individual, such as a telephone number, email address,
current location, etc. On the other hand, the social media
policy's aim is to set standards for acceptable actions and
ensure that users do not expose social media platforms to legal
or public humiliation issues.
These regulations include guidelines on using the platform
for social networking, and guidelines on what kinds of
knowledge should be exchanged. Nearly all social media
policies contain limits on disclosure of sensitive or proprietary
company information or something that could influence
others. The incorrect use of social media, particularly users
who have no or limited cyber culture, may face the user to
attack or hack.
About 3.48 billion active social media users now exist,
making social media an inevitable part of life strategy [1].
Social media network users can share various pieces of
personal information with others when people upload their
images, share their birth date, reveal their phone number and
write their current address. Sharing such personal data will
lead to misuse of the data. For example, some users exchange
profile information that includes their full name, telephone
number, and other sensitive details. Hacking uses one of the
users ' social network account and the hacker can misuse the
information for blackmailing the user.
While comparing the most popular social networks, it's
important to evaluate them by active account usage, not just
by the number of user accounts. Research has shown that
some social networks are rising faster than others, although
others are in decline now. Popular examples of social media
sites are Facebook, Twitter, Instagram, etc.
Nowadays, Facebook is one of the most popular social
media in use around the world. In 2019, Facebook announced
that they have more than 2.38 billion active monthly users [1].
The network enables users to create profile pages where they
can view themselves, post photos etc. Facebook also allows
various apps to be used inside the network, from fortune
cookies to messenger. Twitter is a microblogging website and
up to one hundred forty characters of short messages may be
added to her or his account[2].
\\
\section{	Social media challenges and security risks}
\hspace*{0.3in}Users exchange a huge amount of personal details on
social networks, making them a target for different types of
Internet attacks, including identity theft, phishing, cyber
bullies, spamming, Web fraud, etc. Social networks provide
hackers with vast opportunities to rob identity. In these types
of attacks, a malicious individual may steal his or her personal
details, including bank accounts, addresses, telephone
numbers, etc. without the user's permission, and using it to
commit cyber-crime. For example, a lot of social networks,
including Facebook, give their users game apps .

   To complete the registration process, such applications
include personal details, like the user’s credit card details,
phone number, email, etc. Of course, when a user shares the
phone number and credit card details the risk of personal
details theft and phishing attacks is increased. In certain cases,
apps that result in the user resorting to redirect the user's
attention to harmful content and damage its credibility.
Some of the most obvious potentially innocuous
possibilities in the sense of social networking may be the
illegal use for promotional purposes of personal details, the
collection of possible friends or the discovery of content that
may be of interest. Such techniques are considered a common
process within social networks, and everybody knows about
the collection, review, and usage of personal information for
various purposes, including commercial usage. For one thing,
it has already verified the transfer of personal data from
different social networks.

One of the main issues for users is that numerous user
specific data leakage can be observed as a consequence of the
social network's failure within the framework of various
initiatives. One causes of significant disruption is hacking user
accounts or lack of accountability, and intercepting all
personal information. When the problem is huge, there will be
more serious issues. There are several possible risks to users,
like computer bugs, malware, Trojan horse, phishing, and
other malicious software, and they can be used to steal
sensitive information from the user[2].
\\



