\documentclass[11pt,a4paper,oneside]{report}
\setlength{\textwidth}{6.25in}
\setlength{\textheight}{8in}
\renewcommand{\baselinestretch}{1.3}
\oddsidemargin 20pt
\evensidemargin 20pt
\topmargin 0pt
\newcommand{\squeezeup}{\vspace{-0.6cm}}
\renewcommand*\contentsname{INDEX}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}
\usepackage{titlesec}
\usepackage{url}
\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage[left=3.81cm,top=2.54cm,right=2.54cm,bottom=3.175cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[font=normalsize,labelfont=bf]{caption}
\usepackage{xcolor}
\usepackage{pdfpages}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{fancybox}
\fancypagestyle{plain}

\fancyhf{}
\fancyhead[LE]{\leftmark}
\rhead[RO]{\scriptsize{Synergizing Quantum Computing and Artificial Intelligence: A Review of Trends and Opportunities}}
\cfoot[LE,RO]{\thepage\\\scriptsize{Department of Computer Engineering, GCOERC, Nashik 2025-26}}
\pagestyle{fancy}

\titleformat{\chapter}[display]
{\normalfont\large\bfseries\centering}{\chaptertitlename\ \thechapter}{14pt}{\large}
\titleformat{\section}{\normalsize \bfseries}{\thesection}{1em}{}

\begin{document}
	
	\include{titlepage}
	\include{certificate}
	\include{unicertificate}
	\include{Abstract}
	\include{Acknowledgement}
	\include{Index}
	\addcontentsline{toc}{chapter}{Index}
	\tableofcontents
	\newpage
	\addcontentsline{toc}{chapter}{List of Figures}
	\listoffigures
	\newpage
	\include{chapter1}
	\include{chapter2}
	\include{chapter3}
	\include{chapter4}
	\include{chapter5}
	\include{chapter6}
	\include{chapter7}
	\include{chapter8}
	\include{chapter9}
	\include{conclusion}
	
	\footnotesize
	\addcontentsline{toc}{chapter}{REFERENCES}
	\renewcommand\bibname{References}
	\begin{thebibliography}{}
		\item[1] Vanessa García Pineda, Alejandro Valencia-Arias, Francisco Eugenio López Giraldo, Edison Andrés Zapata-Ochoa, "Integrating Artificial Intelligence and Quantum Computing: A Systematic Literature Review of Features and Applications," 2025. [Online]. Available: https://www.sciencedirect.com/science/article/pii/S266630742500035X.  
		
		\item[2] Ololade Funke Olaitan, Samuel Oluwabukunmi Ayeni, Adedapo Olosunde, Francis Chukwudalu Okeke, Ugochukwu Udonna Okonkwo, Chukwuemeka George Ochieze, Osinachi Victor Chukwujama, Ogheneruemu Nathaniel Akatakpo, "Quantum Computing and Artificial Intelligence: A Review of Quantum Machine Learning Algorithms," Path of Science, vol. 10, no. 6, 2024. [Online]. Available: https://pathofscience.org/index.php/ps/article/view/3541.  
		
		\item[3] Devadas RM, T S., "Quantum Machine Learning: A Comprehensive Review of Integrating AI with Quantum Computing for Computational Advancements," Journal of Computational Science, 2024. [Online]. Available: https://pubmed.ncbi.nlm.nih.gov/40331033/.  
		
		\item[4] T. Crosta, L. Rebón, F. Vilariño, J. M. Matera, M. Bilkis, "Automatic Re-calibration of Quantum Devices by Reinforcement Learning," 2024. [Online]. Available: https://arxiv.org/abs/2404.10726.  
		
		\item[5] G. Pascoal, J. P. Fernandes and R. Abreu, "Deep Reinforcement Learning Strategies for Noise-Adaptive Qubit Routing," IEEE Transactions on Quantum Engineering, 2024. [Online]. Available: https://ieeexplore.ieee.org/document/10646540/.  
		
		\item[6] Jin, Yirong, "Google's 'Willow' Quantum Processor: New RCS Record, and First Error Correction Below the Surface Code Threshold," Quantum, vol. 9, 2025. [Online]. Available: https://linkinghub.elsevier.com/retrieve/pii/S2666675825001456.  
		
		\item[7] Dominic Widdows, Willie Aboumrad, Dohun Kim, Sayonee Ray, Jonathan Mei, "Natural Language, AI, and Quantum Computing in 2024: Research Ingredients and Directions in QNLP," 2024. [Online]. Available: https://arxiv.org/abs/2403.19758.  
		
		\item[8] Pallavi Gundala, Prasanna Kumar Rangarajan, "Quantum Natural Language Processing and Its Applications," Frontiers in Computer Science, 2025. [Online]. Available: https://www.frontiersin.org/journals/computer-science/articles/10.3389/fcomp.2025.1464122/full.  
		
		\item[9] Quantum News, "Quantum Computing Applications: Drug Discovery," Quantum Zeitgeist, 2024. [Online]. Available: https://quantumzeitgeist.com/quantum-computing-applications-drug-discovery/.  
		
		\item[10] M. Munshi, R. Gupta, N. K. Jadav, S. Tanwar, A. Nair and D. Garg, "Quantum Machine Learning-Based Lung Cancer Prediction Framework for Healthcare 4.0," IEEE Access, 2024. [Online]. Available: https://ieeexplore.ieee.org/document/10673456/.  
		
		\item[11] Sanjai Vudugula, Sanath Kumar Chebrolu, "Quantum AI-Driven Business Intelligence for Carbon-Neutral Supply Chains," African Journal of Advanced Technology and Engineering Studies, vol. 2, no. 1, 2024. [Online]. Available: https://ajates-scholarly.com/index.php/ajates/article/view/16.  
		
		\item[12] Google Quantum AI and Collaborators, "Quantum Error Correction Below the Surface Code Threshold," Nature, vol. 631, no. 8021, 2024. [Online]. Available: https://www.nature.com/articles/s41586-024-08449-y.  
		
		\item[13] Fasco , Pamba Shatson, "Beyond Boolean Epistemology: A Non-Classical Logic Approach to Understanding Knowledge Formation in Quantum Computing Systems," International Journal of Scientific Research and Management, vol. 12, no. 8, 2024. [Online]. Available: https://ijsrm.net/index.php/ijsrm/article/view/6089.  
		
		\item[14] McKinsey \& Company, "The Year of Quantum: From Concept to Reality in 2025," 2025. [Online]. Available: https://www.mckinsey.com/capabilities/mckinsey-digital/our-insights/the-year-of-quantum-from-concept-to-reality-in-2025.  
		
		\item[15] SpinQ Team, "Quantum Artificial Intelligence: Unleashing the Next Frontier in Computing," SpinQuanta News, 2024. [Online]. Available: https://www.spinquanta.com/news-detail/quantum-artificial-intelligence-unleashing-the-next-frontier-in-computing-with-spinq.  
	\end{thebibliography}
	
\end{document}